---
title: "Processing all the final set of datasets for using with `iSEE`"
author:
- name: Federico Marini^[marinif@uni-mainz.de]
  affiliation: Institute of Medical Biostatistics, Epidemiology and Informatics ([IMBEI, Mainz](https://www.unimedizin-mainz.de/imbei/imbei/welcome-page.html?L=1))
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: show
    theme: lumen
---

# From Python (AnnData) to h5 format for SingleCellExperiment

Reading in, via `zellkonverter`.

```{r}
library(zellkonverter)

sce_Bcells_h5ad <- readH5AD("final_set/Bcells_covid-19.h5ad")
sce_Monocytes_h5ad <- readH5AD("final_set/Monocytes_covid-19.h5ad")
sce_NKcells_h5ad <- readH5AD("final_set/NKcells_covid-19.h5ad")
sce_Tcells_h5ad <- readH5AD("final_set/Tcells_covid-19.h5ad")
```

Editing the names of the reduced dimension slots for better readability

```{r}
reducedDimNames(sce_Bcells_h5ad) <- toupper(gsub(pattern = "^X_", "", reducedDimNames(sce_Bcells_h5ad)))
reducedDimNames(sce_Monocytes_h5ad) <- toupper(gsub(pattern = "^X_", "", reducedDimNames(sce_Monocytes_h5ad)))
reducedDimNames(sce_NKcells_h5ad) <- toupper(gsub(pattern = "^X_", "", reducedDimNames(sce_NKcells_h5ad)))
reducedDimNames(sce_Tcells_h5ad) <- toupper(gsub(pattern = "^X_", "", reducedDimNames(sce_Tcells_h5ad)))

reducedDimNames(sce_Bcells_h5ad) 
reducedDimNames(sce_Monocytes_h5ad) 
reducedDimNames(sce_NKcells_h5ad) 
reducedDimNames(sce_Tcells_h5ad) 
```

Same goes for the slot X, which we can rename logcounts

```{r}
assayNames(sce_Bcells_h5ad) <- "logcounts"
assayNames(sce_Monocytes_h5ad) <- "logcounts"
assayNames(sce_NKcells_h5ad) <- "logcounts"
assayNames(sce_Tcells_h5ad) <- "logcounts"
```


Writing back to a format that can be taken up right away as SingleCellExperiment

```{r}
HDF5Array::saveHDF5SummarizedExperiment(sce_Bcells_h5ad, dir = "see_finalset_Bcells", replace = TRUE)
HDF5Array::saveHDF5SummarizedExperiment(sce_Monocytes_h5ad, dir = "see_finalset_Monocytes", replace = TRUE)
HDF5Array::saveHDF5SummarizedExperiment(sce_NKcells_h5ad, dir = "see_finalset_NKcells", replace = TRUE)
HDF5Array::saveHDF5SummarizedExperiment(sce_Tcells_h5ad, dir = "see_finalset_Tcells", replace = TRUE)
```

Test that it is correctly read in again

```{r}
sce_Bcells <- HDF5Array::loadHDF5SummarizedExperiment("see_finalset_Bcells")
sce_Monocytes <- HDF5Array::loadHDF5SummarizedExperiment("see_finalset_Monocytes")
sce_NKcells <- HDF5Array::loadHDF5SummarizedExperiment("see_finalset_NKcells")
sce_Tcells <- HDF5Array::loadHDF5SummarizedExperiment("see_finalset_Tcells")

sce_Bcells
sce_Monocytes
sce_NKcells
sce_Tcells

scater::plotUMAP(sce_Bcells, colour_by="cluster_annotation")
scater::plotUMAP(sce_Monocytes, colour_by="cluster_annotation")
scater::plotUMAP(sce_NKcells, colour_by="cluster_annotation")
scater::plotUMAP(sce_Tcells, colour_by="cluster_annotation")
```

# Setting up iSEE for these datasets

Transfer these to the server where the iSEE apps are set up and running

```
scp -r see_finalset_Bcells root@shiny.imbei.uni-mainz.de:/srv/shiny-server/iSEE_covidIT_Bcells/see_finalset_Bcells
scp -r see_finalset_Monocytes root@shiny.imbei.uni-mainz.de:/srv/shiny-server/iSEE_covidIT_Monocytes/see_finalset_Monocytes
scp -r see_finalset_NKcells root@shiny.imbei.uni-mainz.de:/srv/shiny-server/iSEE_covidIT_NKcells/see_finalset_NKcells
scp -r see_finalset_Tcells root@shiny.imbei.uni-mainz.de:/srv/shiny-server/iSEE_covidIT_Tcells/see_finalset_Tcells
```


```{r}
library(iSEE)
iSEE(sce_Bcells)
iSEE(sce_Monocytes)
iSEE(sce_NKcells)
iSEE(sce_Tcells)
```


```{r eval=FALSE}

initial <- list()



iSEE(sce, initial = initial)
```

# Session info {-}

```{r}
sessionInfo()
```


